---
title: "Metalabeling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      results = "",
                      message = FALSE,
                      warning = FALSE)
```

# Loading libraries
```{r echo=FALSE, results = "hide"}
library(rvest)
library(stringr)
library(data.table)
library(xts)
library(PerformanceAnalytics)
library(quantmod)
library(portfolioBacktest)
library(TTR)
library(ggfortify)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(reshape2)
library(randomForest)
library(caret)

library(CVXR)

setwd("~/Dropbox/meta-labeling\ (w\ Guillermo)/Code/Current")

source("tables.R")
source("cusum.R")
source("labels.R")
source("features.R")
source("ROC.R")
source("misc.R")
source("plots.R")

source("GMVP/primary_model_GMVP.R")
source("GMVP/secondary_model_GMVP.R")
source("GMVP/primary_model_ROC.R")
source("GMVP/auxiliary_functions_GMVP.R")
source("GMVP/full_returns_GMVP.R")
source("GMVP/discrete_returns_GMVP.R")
```

```{r}
set.seed(1)
r1 <- rnorm(100, mean = 0.01, sd = 0.02)
mu_old <- mean(r1)
sigma_old <- sd(r1)
mu_old/sigma_old*sqrt(length(r1))


mu_new <- sum(r1)/252
sigma_new <- sd(c(rep(0, 252 - length(r1)), r1))
mu_new/sigma_new*sqrt(252)
```

```{r echo=FALSE}
load(file = "~/Dropbox/Otros/clean_returns_GMVP.RData") 
GMVP_prices <- cumprod(1 + GMVP_returns)
GMVP_MA <- SMA(GMVP_prices, n = 20)
GMVP_signal <- lag(GMVP_prices >= GMVP_MA)
GMVP_signal[GMVP_signal == 0] <- - 1
index(GMVP_signal) <- as.Date(index(GMVP_signal))

# HYPERPARAMETERS _________
tc <- 5*0.01*1e-2  # 5 bps
window_length <- 20
holding_time <- 10
# _________________________
```

# Primary Model - (ML)

## Features and labels
```{r echo=FALSE}
X_primary_model <- get_features_primary_model(GMVP_returns, 
                                              window_length = 20,
                                              threshold = 1.5)

call_labels <- get_labels_primary_model(GMVP_returns, 
                                        X_primary_model,
                                        window_length = window_length,
                                        max_time = holding_time)
 
y_primary_model <- call_labels$labels
realized_returns_primary_model <- call_labels$realized_returns

data_primary_model <- na.omit(cbind(X_primary_model, y_primary_model))

N_split <- as.integer(0.8*nrow(data_primary_model))
N_split_train <- as.integer(0.8*N_split)

train_data_primary_model <- data_primary_model[1:N_split_train, ]
validation_data_primary_model <- data_primary_model[(N_split_train + 1):N_split, ]
test_data_primary_model <- data_primary_model[(N_split + 1):nrow(data_primary_model), ]

train_returns_primary_model <- realized_returns_primary_model[1:N_split_train]
validation_returns_primary_model <-
  realized_returns_primary_model[(N_split_train + 1):N_split]
test_returns_primary_model <- 
  realized_returns_primary_model[-c(1:N_split)]

set.seed(1998)
random_forest_primary_model <- train(label~. , train_data_primary_model, 
                                     method = "rf", importance = TRUE)

importance(random_forest_primary_model$finalModel)

predicted_train <- random_forest_primary_model$finalModel$predicted
predicted_train <- as.xts(predicted_train,
                          order.by = index(train_data_primary_model))

predicted_validation <- predict(random_forest_primary_model, 
                                validation_data_primary_model)
predicted_validation <- as.xts(predicted_validation,
                               order.by = as.Date(names(predicted_validation)))

predicted_test <- predict(random_forest_primary_model, test_data_primary_model)
predicted_test <- as.xts(predicted_test,
                         order.by = as.Date(names(predicted_test)))
```

## Parameter tuning (Primary Model)
```{r echo=FALSE}
thresholds <- seq(from = 0, to = 1, length.out = 20)
all_SR_primary_model <- all_num_discrete_returns <- c()
for (thr in thresholds) {
  SR <- Sharpe_Ratio_from_predictions(returns = GMVP_returns,
                                      enter = predicted_validation > thr,
                                      window_length = window_length,
                                      max_time = holding_time,
                                      tc = tc,
                                      verbose = FALSE)
    
  if (length(SR) == 0) SR <- -Inf
  if (is.na(SR)) SR <- -Inf
  all_SR_primary_model <- c(all_SR_primary_model, SR)
  
  discrete_returns <- get_discrete_returns(returns = GMVP_returns,
                                           enter = predicted_validation > thr,
                                           window_length = window_length,
                                           max_time = holding_time,
                                           tc = tc)
  
  n_disc <- length(discrete_returns)
  if (length(n_disc) == 0) n_disc <- 0
  if (is.na(n_disc)) n_disc <- 0
  all_num_discrete_returns <- c(all_num_discrete_returns, n_disc)
}

# ________ IGNORE ________
dd <- round(data.frame(cbind(thresholds, 
                             all_num_discrete_returns, 
                             all_SR_primary_model)), 4)

dd$`Enough observations` <- 
  dd$all_num_discrete_returns > median(all_num_discrete_returns)/2

ggplot(dd, aes(x=thresholds, y=all_SR_primary_model, 
               color=`Enough observations`)) +
  geom_point() + xlab("Threshold") + ylab("SR") +
  ggtitle("SR Primary model (CV)")

dd <- as.matrix(dd)
iniStr <- ""
for (i in 1:nrow(dd)) {
  auxStr <- paste(dd[i, 1], dd[i, 2], dd[i, 3], sep = " & ")
  auxStr <- paste(auxStr, "\\\\ ", sep = "")
  iniStr <- paste(iniStr, "\n ", auxStr, sep = "")
}
cat(iniStr)
# _______________________

print(round(data.frame(cbind(thresholds, 
                             all_num_discrete_returns, 
                             all_SR_primary_model)), 4))

min_n_ret <- median(all_num_discrete_returns)/2
ind_reliable <- which(all_num_discrete_returns > min_n_ret)
all_SR_primary_model <- all_SR_primary_model[ind_reliable]

points_SR <- rank(all_SR_primary_model)

best_thr_m1 <- thresholds[max(which(points_SR == max(points_SR)))]

SR_validation <- all_SR_primary_model[match(best_thr_m1, thresholds)]

SR_test <- Sharpe_Ratio_from_predictions(returns = GMVP_returns,
                                         enter = (predicted_test > best_thr_m1),
                                         window_length = window_length,
                                         max_time = holding_time,
                                         tc = tc,
                                         verbose = FALSE)

raw_SR_test <- Sharpe_Ratio_from_predictions(returns = GMVP_returns,
                                             enter = (predicted_test > -1),
                                             window_length = window_length,
                                             max_time = holding_time,
                                             tc = tc,
                                             verbose = FALSE)

BH_SR_test <- SharpeRatio.annualized(GMVP_returns[index(test_data_primary_model)])
BH_SR_test <- as.numeric(BH_SR_test)

BH_SR_validation <- 
  SharpeRatio.annualized(GMVP_returns[index(validation_data_primary_model)])
BH_SR_validation <- as.numeric(BH_SR_validation)
```

## Results Primary Model
```{r echo=FALSE}
cat(paste(paste("Sharpe Ratio w/ lowest points (Validation Set) =", 
                round(SR_validation, 4)),
          paste("Sharpe Ratio (Validation) - B&H =", 
                round(BH_SR_validation, 4)),
          paste("Sharpe Ratio (Test) - B&H =", 
                round(BH_SR_test, 4)),
          paste("Sharpe Ratio (Test) - triple barrier =", 
                round(raw_SR_test, 4)),
          paste("Sharpe Ratio (Test) - primary model (lowest points) =", 
                round(SR_test, 4)),
          sep = "\n"))
```

# Secondary Model - (ML)

## Features and labels
```{r echo=FALSE}
# Features

# Predictions from primary model
predictions_primary_model <- c(predicted_train,
                               predicted_validation,
                               predicted_test)

# Features from returns
X_secondary_model <- get_features(GMVP_returns, 
                                  signal = GMVP_signal,
                                  MA = GMVP_MA)[[1]]
# Solving UTC problems
index(X_secondary_model) <- as.Date(index(X_secondary_model))

X_secondary_model <- na.omit(cbind(predictions_primary_model, X_secondary_model))


# Labels

y_secondary_model <- get_labels_secondary_model(realized_returns_primary_model,
                                                predictions_primary_model,
                                                best_thr_m1)

# Merging Features w/ Labels
data_secondary_model <- na.omit(cbind(X_secondary_model, y_secondary_model))

# Train, Validation and Test Data
train_data_secondary_model <- 
  data_secondary_model[index(train_data_primary_model)]

validation_data_secondary_model <- 
  data_secondary_model[index(validation_data_primary_model)]

test_data_secondary_model <- 
  data_secondary_model[index(test_data_primary_model)]

set.seed(1998)
random_forest_secondary_model <- train(label~. , train_data_secondary_model, 
                                       method = "rf", importance = TRUE)

importance(random_forest_secondary_model$finalModel)

predicted_validation_m2 <- 
  predict(random_forest_secondary_model, validation_data_secondary_model)
predicted_validation_m2 <- 
  as.xts(predicted_validation_m2, 
         order.by = as.Date(names(predicted_validation_m2)))

predicted_test_m2 <-
  predict(random_forest_secondary_model, test_data_secondary_model)
predicted_test_m2 <- 
  as.xts(predicted_test_m2,
         order.by = as.Date(names(predicted_test_m2)))
```

## Parameter tuning (Meta Model)
```{r echo=FALSE}
thresholds <- seq(from = 0, to = 1, length.out = 20)
all_SR_secondary_model <- all_num_discrete_returns <- c()
for (thr in thresholds) {
  enter_decision <- enter_decision_2_models(predicted_validation, 
                                            predicted_validation_m2,
                                            best_thr_m1,
                                            thr)
  
  SR <- Sharpe_Ratio_from_predictions(returns = GMVP_returns,
                                      enter = enter_decision,
                                      window_length = window_length,
                                      max_time = holding_time,
                                      tc = tc,
                                      threshold = thr,
                                      verbose = FALSE)
  
  if (length(SR) == 0) SR <- -Inf
  all_SR_secondary_model <- c(all_SR_secondary_model, SR)
  
  discrete_returns <- get_discrete_returns(returns = GMVP_returns,
                                           enter = enter_decision,
                                           window_length = window_length,
                                           max_time = holding_time,
                                           tc = tc)
  
  n_disc <- length(discrete_returns)
  if (length(n_disc) == 0) n_disc <- 0
  if (is.na(n_disc)) n_disc <- 0
  all_num_discrete_returns <- c(all_num_discrete_returns, n_disc)
}

# ________ IGNORE ________
dd <- round(data.frame(cbind(thresholds, 
                             all_num_discrete_returns, 
                             all_SR_secondary_model)), 4)

dd$`Enough observations` <- 
  dd$all_num_discrete_returns > median(all_num_discrete_returns)/2

ggplot(dd, aes(x=thresholds, y=all_SR_secondary_model, 
               color=`Enough observations`)) +
  geom_point() + xlab("Threshold") + ylab("SR") +
  ggtitle("SR Secondary model (CV)")

dd <- as.matrix(dd)
iniStr <- ""
for (i in 1:nrow(dd)) {
  auxStr <- paste(dd[i, 1], dd[i, 2], dd[i, 3], sep = " & ")
  auxStr <- paste(auxStr, "\\\\ ", sep = "")
  iniStr <- paste(iniStr, "\n ", auxStr, sep = "")
}
cat(iniStr)
# _______________________

print(round(data.frame(cbind(thresholds, 
                             all_num_discrete_returns, 
                             all_SR_secondary_model)), 4))

min_n_ret <- median(all_num_discrete_returns)/2
ind_reliable <- which(all_num_discrete_returns > min_n_ret)
all_SR_secondary_model <- all_SR_secondary_model[ind_reliable]

points_SR <- rank(all_SR_secondary_model)

best_thr_m2 <- thresholds[max(which(points_SR == max(points_SR)))]
# Sharpe Ratios

SR_validation_m2 <- all_SR_secondary_model[match(best_thr_m2, thresholds)]

enter_decision <- enter_decision_2_models(predicted_test, 
                                          predicted_test_m2,
                                          best_thr_m1,
                                          best_thr_m2)

SR_test_m2 <- Sharpe_Ratio_from_predictions(returns = GMVP_returns,
                                            enter = enter_decision,
                                            window_length = window_length,
                                            max_time = holding_time,
                                            tc = tc,
                                            verbose = FALSE)

Sharpe_Ratio_from_predictions(returns = GMVP_returns,
                              enter = (predicted_validation > -1),
                              window_length = window_length,
                              max_time = holding_time,
                              tc = tc,
                              verbose = FALSE)
```

## Results Meta model
```{r echo=FALSE}
cat(paste(paste("Sharpe Ratio (Validation) - secondary model =", 
                round(SR_validation_m2, 4)),
          paste("Sharpe Ratio (Validation) - B&H =", 
                round(BH_SR_validation, 4)),
          paste("Sharpe Ratio (Test) - B&H =", 
                round(BH_SR_test, 4)),
          paste("Sharpe Ratio (Test) - triple barrier =", 
                round(raw_SR_test, 4)),
          paste("Sharpe Ratio (Test) - primary model (lowest points) =",
                round(SR_test, 4)),
          paste("Sharpe Ratio (Test) - secondary model (lowest points) =",
                round(SR_test_m2, 4)),
          sep = "\n"))
```

## Plots Meta model
## Validation Set
```{r echo=FALSE}
full_returns_3b <- get_full_returns(returns = GMVP_returns, 
                                    enter = predicted_validation > -1,
                                    window_length = window_length,
                                    max_time = holding_time,
                                    tc = tc)

full_returns_m1 <- get_full_returns(returns = GMVP_returns, 
                                    enter = predicted_validation > best_thr_m1,
                                    window_length = window_length,
                                    max_time = holding_time,
                                    tc = tc)

enter_decision <- enter_decision_2_models(predicted_validation, 
                                          predicted_validation_m2,
                                          best_thr_m1,
                                          best_thr_m2)
index(enter_decision) <- as.Date(index(enter_decision))

full_returns_m2 <- get_full_returns(returns = GMVP_returns, 
                                    enter = enter_decision,
                                    window_length = window_length,
                                    max_time = holding_time,
                                    tc = tc)

start_t1 <- match(index(validation_data_secondary_model)[1], 
                  index(GMVP_returns))
end_t1 <- match(tail(index(validation_data_secondary_model), 1), 
                index(GMVP_returns))

baseCase <- zeroCase <- GMVP_returns[start_t1:end_t1]
zeroCase[] <- 0
ret2Graph_3b <- ret2Graph_m1 <- ret2Graph_m2 <- zeroCase

p2_1 <- plot_portfolios(cumprod(1 + baseCase),
                        title = "GMVP (Validation)", 
                        show_legend = FALSE)

ret2Graph_3b[index(full_returns_3b)] <- full_returns_3b

p2_2 <- plot_portfolios(cumprod(1 + ret2Graph_3b), 
                        title = "Triple Barrier (Validation)", 
                        show_legend = FALSE)

ret2Graph_m1[index(full_returns_m1)] <- full_returns_m1

p2_3 <- plot_portfolios(cumprod(1 + ret2Graph_m1), 
                        title = "Primary Model (Validation)", 
                        show_legend = FALSE)

ret2Graph_m2[index(full_returns_m2)] <- full_returns_m2

p2_4 <- plot_portfolios(cumprod(1 + ret2Graph_m2), 
                        title = "Meta Model (Validation)", 
                        show_legend = FALSE)

grid.arrange(p2_1, p2_2,
             p2_3, p2_4,
             nrow = 2, ncol = 2)

ret_all_valid <- cbind(baseCase,
                       ret2Graph_3b,
                       ret2Graph_m1,
                       ret2Graph_m2)
colnames(ret_all_valid) <- c("GMVP", "Triple Barrier",
                             "Primary Model", "Meta Model")
```

## Test Set
```{r echo=FALSE}
full_returns_3b <- get_full_returns(returns = GMVP_returns, 
                                    enter = predicted_test > -1,
                                    window_length = window_length,
                                    max_time = holding_time,
                                    tc = tc)

full_returns_m1 <- get_full_returns(returns = GMVP_returns, 
                                    enter = predicted_test > best_thr_m1,
                                    window_length = window_length,
                                    max_time = holding_time,
                                    tc = tc)

enter_decision <- enter_decision_2_models(predicted_test, 
                                          predicted_test_m2,
                                          best_thr_m1,
                                          best_thr_m2)
index(enter_decision) <- as.Date(index(enter_decision))

full_returns_m2 <- get_full_returns(returns = GMVP_returns, 
                                    enter = enter_decision,
                                    window_length = window_length,
                                    max_time = holding_time,
                                    tc = tc)

start_t1 <- match(index(test_data_secondary_model)[1], index(GMVP_returns))
end_t1 <- match(tail(index(test_data_secondary_model), 1), index(GMVP_returns))

baseCase <- zeroCase <- GMVP_returns[start_t1:end_t1]
zeroCase[] <- 0
ret2Graph_3b <- ret2Graph_m1 <- ret2Graph_m2 <- zeroCase

p2_1 <- plot_portfolios(cumprod(1 + baseCase),
                        title = "GMVP (Test)", show_legend = FALSE)

ret2Graph_3b[index(full_returns_3b)] <- full_returns_3b

p2_2 <- plot_portfolios(cumprod(1 + ret2Graph_3b), 
                        title = "Triple Barrier (Test)", show_legend = FALSE)

ret2Graph_m1[index(full_returns_m1)] <- full_returns_m1

p2_3 <- plot_portfolios(cumprod(1 + ret2Graph_m1), 
                        title = "Primary Model (Test)", show_legend = FALSE)

ret2Graph_m2[index(full_returns_m2)] <- full_returns_m2

p2_4 <- plot_portfolios(cumprod(1 + ret2Graph_m2), 
                        title = "Meta Model (Test)", show_legend = FALSE)

grid.arrange(p2_1, p2_2,
             p2_3, p2_4,
             nrow = 2, ncol = 2)

ret_all_tst <- cbind(baseCase,
                     ret2Graph_3b,
                     ret2Graph_m1,
                     ret2Graph_m2)
colnames(ret_all_tst) <- c("GMVP", "Triple Barrier",
                           "Primary Model", "Meta Model")

chart.Drawdown(ret_all_tst, main = "Drawdown of Models (out-of-sample)", 
               legend.loc = "bottomleft", colorset = rainbow6equal)
```

## ROC
```{r echo=FALSE}
aux_signal <- GMVP_signal
aux_signal[] <- 1

ROC_train <- ROC_validation <- ROC_test <- data.frame("FPR" = c(), "TPR" = c())
thresholds <- seq(from = 0, to = 1, length.out = 20)


enter_decision <- enter_decision_2_models(predicted_test, 
                                          predicted_test_m2,
                                          best_thr_m1,
                                          -1)

discrete_returns <- get_discrete_returns(returns = GMVP_returns,
                                         enter = enter_decision,
                                         window_length = window_length,
                                         max_time = holding_time,
                                         tc = tc)

enter_decision_v <- enter_decision_2_models(predicted_validation, 
                                            predicted_validation_m2,
                                            best_thr_m1,
                                            -1)

discrete_returns_v <- get_discrete_returns(returns = GMVP_returns,
                                           enter = enter_decision_v,
                                           window_length = window_length,
                                           max_time = holding_time,
                                           tc = tc)

for (i in 1:length(thresholds)) {

  new_point <- get_TPR_and_FPR(aux_signal, discrete_returns, 
                               predicted_test_m2, thresholds[i])
  
  new_point <- c(new_point$FPR, new_point$TPR)
  
  ROC_test <- rbind(ROC_test, new_point)
  
  new_point <- get_TPR_and_FPR(aux_signal, discrete_returns_v, 
                               predicted_validation_m2, thresholds[i])
  
  new_point <- c(new_point$FPR, new_point$TPR)
  
  ROC_validation <- rbind(ROC_validation, new_point)
}

# colnames(ROC_train) <- colnames(ROC_test) <- c("FPR", "TPR")
colnames(ROC_test) <- c("FPR", "TPR")
colnames(ROC_validation) <- c("FPR", "TPR")
type_portfolio <- "GMVP"

print(ggplot(ROC_validation, mapping = aes(x = FPR, y = TPR, color = "Validation")) +
        geom_line(size = 1.5, alpha = 0.7) +
        geom_line(ROC_test, mapping = aes(x = FPR, y = TPR, color = "Test"), 
                  size = 1.5, alpha = 0.7) +
        geom_line(mapping = aes(x = seq(0, 1, length.out = 20), 
                                y = seq(0, 1, length.out = 20), 
                                color = "Random"),
                  linetype = "dotted") +
        labs(title = paste("ROC curve", type_portfolio, "portfolio"), 
             x = "False Positive Rate", 
             y = "True Positive Rate") + 
        scale_color_manual(name = "", 
                           values = c("Validation" = "skyblue2", 
                                      "Test" = "olivedrab2", 
                                      "Random" = "black")))




```

# Primary Model - (MA)

# Secondary Model - (MA)

## Features and labels
```{r echo=FALSE}
# Features

# Features from returns
X_secondary_model <- get_features(GMVP_returns, 
                                  signal = GMVP_signal,
                                  MA = GMVP_MA)[[1]]
# Solving UTC problems
index(X_secondary_model) <- as.Date(index(X_secondary_model))


# Labels
thr_prueba_m1 <- seq(0.25, 2, length.out = 6)
call_labels <- get_labels(GMVP_returns, 
                          max_time = holding_time, 
                          tc = tc,
                          threshold = thr_prueba_m1[3],
                          ptsl = c(2, 2), 
                          signal = GMVP_signal)

y_secondary_model <- call_labels$label[[1]]
colnames(y_secondary_model) <- "label"

returns_secondary_model <- call_labels$realized_returns[[1]]
exit_secondary_model <- call_labels$exit[[1]]

# Merging Features w/ Labels
data_secondary_model <- na.omit(cbind(X_secondary_model, y_secondary_model))

N_split <- as.integer(0.8*nrow(data_secondary_model))
N_split_train <- as.integer(0.8*N_split)
N_total <- nrow(data_secondary_model)

# Train, Validation and Test Data
train_data_secondary_model <- data_secondary_model[1:N_split_train, ]
validation_data_secondary_model <- data_secondary_model[(N_split_train + 1):N_split, ]
test_data_secondary_model <- data_secondary_model[(N_split + 1):N_total, ]

train_returns_secondary_model <- 
  returns_secondary_model[index(train_data_secondary_model)]
train_exit_secondary_model <- 
  exit_secondary_model[index(train_data_secondary_model)]

validation_returns_secondary_model <- 
  returns_secondary_model[index(validation_data_secondary_model)]
validation_exit_secondary_model <- 
  exit_secondary_model[index(validation_data_secondary_model)]

test_returns_secondary_model <- 
  returns_secondary_model[index(test_data_secondary_model)]
test_exit_secondary_model <- 
  exit_secondary_model[index(test_data_secondary_model)]

# Training Random Forest
set.seed(1998)
random_forest_secondary_model <- randomForest(label~. , train_data_secondary_model, 
                                              importance = TRUE)

importance(random_forest_secondary_model)

predicted_train_m2 <- 
  random_forest_secondary_model$predicted
predicted_train_m2 <- 
  as.xts(predicted_train_m2, 
         order.by = index(train_data_secondary_model))

predicted_validation_m2 <- 
  predict(random_forest_secondary_model, validation_data_secondary_model)
predicted_validation_m2 <- 
  as.xts(predicted_validation_m2, 
         order.by = as.Date(names(predicted_validation_m2)))

predicted_test_m2 <-
  predict(random_forest_secondary_model, test_data_secondary_model)
predicted_test_m2 <- 
  as.xts(predicted_test_m2,
         order.by = as.Date(names(predicted_test_m2)))



# _____ To delete _____

predicted_test_m1 <- GMVP_signal[index(predicted_test_m2)]
predicted_test_mm <- predicted_test_m1*round(predicted_test_m2)

yM1Tst <- (
  realized_returns_primary_model[index(predicted_test_m2)]*predicted_test_m1
  ) > 0

# _____ M1 _____

TP <- sum(yM1Tst)
FP <- sum(yM1Tst == 0)
TN <- 0
FN <- 0

recall <- TP/(TP + FN)
precision <- TP/(TP + FP)
f1Score <- 2/(1/recall + 1/precision)

# _______________

# _____ MM _____

TP <- sum(predicted_test_mm != 0 & yM1Tst == 1)
FP <- sum(predicted_test_mm != 0 & yM1Tst == 0)
TN <- sum(predicted_test_mm == 0 & yM1Tst == 0)
FN <- sum(predicted_test_mm == 0 & yM1Tst == 1)

recall <- TP/(TP + FN)
precision <- TP/(TP + FP)
f1Score <- 2/(1/recall + 1/precision)

# _______________
# _______________

predicted_val_m1 <- GMVP_signal[index(predicted_validation_m2)]
predicted_val_mm <- predicted_val_m1*round(predicted_validation_m2)

yM1Val <- (
  realized_returns_primary_model[index(predicted_validation_m2)]*predicted_val_m1
  ) > 0

# _____ M1 _____

TP <- sum(yM1Val)
FP <- sum(yM1Val == 0)
TN <- 0
FN <- 0

recall <- TP/(TP + FN)
precision <- TP/(TP + FP)
f1Score <- 2/(1/recall + 1/precision)

# _______________

# _____ MM _____

TP <- sum(predicted_val_mm != 0 & yM1Val == 1)
FP <- sum(predicted_val_mm != 0 & yM1Val == 0)
TN <- sum(predicted_val_mm == 0 & yM1Val == 0)
FN <- sum(predicted_val_mm == 0 & yM1Val == 1)

recall <- TP/(TP + FN)
precision <- TP/(TP + FP)
f1Score <- 2/(1/recall + 1/precision)

# _______________
# _______________
```

## Parameter tuning (Meta Model)
```{r echo=FALSE}
thresholds <- seq(from = 0, to = 1, length.out = 20)
all_SR_secondary_model <- all_num_discrete_returns <- c()
realized_vol <- get_daily_vol(GMVP_returns, window_length)
start_candidates <- get_start_position(GMVP_returns, 
                                       threshold = thr_prueba_m1[3], 
                                       realized_vol)

start_candidates_validation <- 
  start_candidates[index(validation_data_secondary_model)]
for (thr in thresholds) {
  thr_candidates <- start_candidates_validation*(predicted_validation_m2 > thr)
  
  call_returns <- get_touch_individual(GMVP_returns, 
                                       start_candidates = thr_candidates,
                                       signal = GMVP_signal,
                                       holding_time = holding_time, 
                                       realized_vol = realized_vol,
                                       tc = tc)
  
  complete_returns <- call_returns$filtered_returns
  discrete_returns <- call_returns$real_returns  # 99
  
  SR <- SR_strategy(complete_returns)
  
  if (length(SR) == 0) SR <- -Inf
  if (is.na(SR)) SR <- -Inf
  all_SR_secondary_model <- c(all_SR_secondary_model, SR)
  
  n_disc <- length(discrete_returns)
  if (length(n_disc) == 0) n_disc <- 0
  if (is.na(n_disc)) n_disc <- 0
  all_num_discrete_returns <- c(all_num_discrete_returns, n_disc)
}

# ________ IGNORE ________
dd <- round(data.frame(cbind(thresholds, 
                             all_num_discrete_returns, 
                             all_SR_secondary_model)), 4)

dd$`Enough observations` <- 
  dd$all_num_discrete_returns > median(all_num_discrete_returns)/2

ggplot(dd, aes(x=thresholds, y=all_SR_secondary_model, 
               color=`Enough observations`)) +
  geom_point() + xlab("Threshold") + ylab("SR") +
  ggtitle("SR Secondary model (CV) - thr_CUSUM = 0.95")

dd <- as.matrix(dd)
iniStr <- ""
for (i in 1:nrow(dd)) {
  auxStr <- paste(dd[i, 1], dd[i, 2], dd[i, 3], sep = " & ")
  auxStr <- paste(auxStr, "\\\\ ", sep = "")
  iniStr <- paste(iniStr, "\n", auxStr, sep = "")
}
cat(iniStr)
# _______________________

print(round(data.frame(cbind(thresholds, 
                             all_num_discrete_returns, 
                             all_SR_secondary_model)), 4))

min_n_ret <- median(all_num_discrete_returns)/2
ind_reliable <- which(all_num_discrete_returns > min_n_ret)
reliable_SR_secondary_model <- all_SR_secondary_model[ind_reliable]

points_SR <- rank(reliable_SR_secondary_model)
SR_validation_m2 <- 
  reliable_SR_secondary_model[max(which(points_SR == max(points_SR)))]

best_thr_m2 <- thresholds[match(SR_validation_m2, all_SR_secondary_model)]

# Sharpe Ratios

# Start candidates
start_candidates_validation_m1 <- 
  start_candidates_validation*(predicted_validation_m2 > -1)
start_candidates_validation_m2 <- 
  start_candidates_validation*(predicted_validation_m2 > best_thr_m2)

start_candidates_test <- start_candidates[index(test_data_secondary_model)]
start_candidates_test_m1 <- start_candidates_test*(predicted_test_m2 > -1)
start_candidates_test_m2 <- start_candidates_test*(predicted_test_m2 > best_thr_m2)

# ____________________

call_returns <- get_touch_individual(GMVP_returns, 
                                     start_candidates = start_candidates_test_m1,
                                     signal = NULL,
                                     holding_time = holding_time, 
                                     realized_vol = realized_vol,
                                     tc = tc)

complete_returns <- call_returns$filtered_returns
  
raw_SR_test <- SR_strategy(complete_returns)

call_returns <- get_touch_individual(GMVP_returns, 
                                     start_candidates = start_candidates_test_m1,
                                     signal = GMVP_signal,
                                     holding_time = holding_time, 
                                     realized_vol = realized_vol,
                                     tc = tc)

complete_returns <- call_returns$filtered_returns
  
SR_test_m1 <- SR_strategy(complete_returns)

call_returns <- get_touch_individual(GMVP_returns, 
                                     start_candidates = start_candidates_test_m2,
                                     signal = GMVP_signal,
                                     holding_time = holding_time, 
                                     realized_vol = realized_vol,
                                     tc = tc)

complete_returns <- call_returns$filtered_returns
  
SR_test_m2 <- SR_strategy(complete_returns)
```

## Results Meta model
```{r echo=FALSE}
cat(paste(paste("Sharpe Ratio w/ lowest points (Validation Set) =", 
                round(SR_validation_m2, 4)),
          paste("Sharpe Ratio (Validation) - B&H =", 
                round(BH_SR_validation, 4)),
          paste("Sharpe Ratio (Test) - B&H =", 
                round(BH_SR_test, 4)),
          paste("Sharpe Ratio (Test) - triple barrier =", 
                round(raw_SR_test, 4)),
          paste("Sharpe Ratio (Test) - primary model (lowest points) =",
                round(SR_test_m1, 4)),
          paste("Sharpe Ratio (Test) - secondary model (lowest points) =",
                round(SR_test_m2, 4)),
          sep = "\n"))
```

## Plots Meta model
## Validation Set
```{r echo=FALSE}
GMVP_touch_3b <-
  get_touch_individual(GMVP_returns, 
                       start_candidates = start_candidates_validation_m1,
                       signal = NULL,
                       holding_time = holding_time, 
                       realized_vol = realized_vol,
                       tc = tc)

GMVP_touch_m1 <-
  get_touch_individual(GMVP_returns, 
                       start_candidates = start_candidates_validation_m1,
                       signal = GMVP_signal,
                       holding_time = holding_time, 
                       realized_vol = realized_vol,
                       tc = tc)

SR_strategy(GMVP_touch_m1$filtered_returns)
tail(cumprod(1 + GMVP_touch_m1$filtered_returns), 1)

GMVP_touch_m2 <-
  get_touch_individual(GMVP_returns, 
                       start_candidates = start_candidates_validation_m2,
                       signal = GMVP_signal,
                       tc = tc,
                       holding_time = holding_time, 
                       realized_vol = realized_vol)


start_t1 <- match(index(validation_data_secondary_model)[1], 
                  index(GMVP_returns))
end_t1 <- match(tail(index(validation_data_secondary_model), 1), 
                index(GMVP_returns))

baseCase <- zeroCase <- GMVP_returns[start_t1:end_t1]
zeroCase[] <- 0
ret2Graph_3b <- ret2Graph_m1 <- ret2Graph_m2 <- zeroCase

p2_1 <- plot_portfolios(cumprod(1 + baseCase),
                        title = "GMVP (Validation)", show_legend = FALSE)

ret2Graph_3b[index(GMVP_touch_3b$filtered_returns)] <- 
  GMVP_touch_3b$filtered_returns

p2_2 <- plot_portfolios(cumprod(1 + ret2Graph_3b), 
                        title = "Triple Barrier (Validation)", 
                        show_legend = FALSE)

ret2Graph_m1[index(GMVP_touch_m1$filtered_returns)] <- 
  GMVP_touch_m1$filtered_returns

p2_3 <- plot_portfolios(cumprod(1 + ret2Graph_m1), 
                        title = "Primary Model (Validation)", 
                        show_legend = FALSE)

ret2Graph_m2[index(GMVP_touch_m2$filtered_returns)] <- 
  GMVP_touch_m2$filtered_returns

p2_4 <- plot_portfolios(cumprod(1 + ret2Graph_m2), 
                        title = "Meta Model (Validation)", show_legend = FALSE)

grid.arrange(p2_1, p2_2,
             p2_3, p2_4,
             nrow = 2, ncol = 2)


ret_all_valid <- cbind(baseCase,
                       ret2Graph_3b,
                       ret2Graph_m1,
                       ret2Graph_m2)
colnames(ret_all_valid) <- c("GMVP", "Triple Barrier",
                             "Primary Model", "Meta Model")

chart.Drawdown(ret_all_valid, main = "Drawdown of Models (Validation)", 
               legend.loc = "bottomleft", colorset = rainbow6equal)

```

## Test Set
```{r echo=FALSE}
GMVP_touch_3b <-
  get_touch_individual(GMVP_returns, 
                       start_candidates = start_candidates_test_m1,
                       signal = NULL,
                       holding_time = holding_time, 
                       realized_vol = realized_vol,
                       tc = tc)
GMVP_touch_m1 <-
  get_touch_individual(GMVP_returns, 
                       start_candidates = start_candidates_test_m1,
                       signal = GMVP_signal,
                       holding_time = holding_time, 
                       realized_vol = realized_vol,
                       tc = tc)

GMVP_touch_m2 <-
  get_touch_individual(GMVP_returns, 
                       start_candidates = start_candidates_test_m2,
                       signal = GMVP_signal,
                       tc = tc,
                       holding_time = holding_time, 
                       realized_vol = realized_vol)


start_t1 <- match(index(test_data_secondary_model)[1], index(GMVP_returns))
end_t1 <- match(tail(index(test_data_secondary_model), 1), index(GMVP_returns))

baseCase <- zeroCase <- GMVP_returns[start_t1:end_t1]
zeroCase[] <- 0
ret2Graph_3b <- ret2Graph_m1 <- ret2Graph_m2 <- zeroCase

p2_1 <- plot_portfolios(cumprod(1 + baseCase),
                        title = "GMVP (Test)", show_legend = FALSE)

ret2Graph_3b[index(GMVP_touch_3b$filtered_returns)] <- 
  GMVP_touch_3b$filtered_returns

p2_2 <- plot_portfolios(cumprod(1 + ret2Graph_3b), 
                        title = "Triple Barrier (Test)", show_legend = FALSE)

ret2Graph_m1[index(GMVP_touch_m1$filtered_returns)] <- 
  GMVP_touch_m1$filtered_returns

p2_3 <- plot_portfolios(cumprod(1 + ret2Graph_m1), 
                        title = "Primary Model (Test)", show_legend = FALSE)

ret2Graph_m2[index(GMVP_touch_m2$filtered_returns)] <- 
  GMVP_touch_m2$filtered_returns

p2_4 <- plot_portfolios(cumprod(1 + ret2Graph_m2), 
                        title = "Meta Model (Test)", show_legend = FALSE)

grid.arrange(p2_1, p2_2,
             p2_3, p2_4,
             nrow = 2, ncol = 2)

ret_all_tst <- cbind(baseCase,
                     ret2Graph_3b,
                     ret2Graph_m1,
                     ret2Graph_m2)
colnames(ret_all_tst) <- c("GMVP", "Triple Barrier",
                           "Primary Model", "Meta Model")

chart.Drawdown(ret_all_tst, main = "Drawdown of Models (out-of-sample)", 
               legend.loc = "bottomleft", colorset = rainbow6equal)

```